Detector_Validation

### 2020-01-15 analysis/analysis_fulldataset.Rmd
separate out preprocessing of main datasets

## Read in data

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos 
flipped_videos <- right_side_up %>%
  filter(right_side_up==1) %>%
  rename(vid_name = video)

@@

### Load SAYCAM metadata from csv file; get metadata from detections .csv
```{r}
metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"

### Load in detections from preprocessed Rdata file; 
```{r eval=FALSE}
 # Could do list of detections  from csv (takes forever, skipping)
# data_file = "../data/all_frames.csv"
# detections=read.csv(data_file)

## rdata is faster
load('../data/openpose_detections.RData')
```

### Preprocess data (doesn't exceute; loads processed data below)
```{r eval=FALSE}
# get shortened video names so they match across all files
all_video_names = as.tibble(unique(detections$vid_name))
all_video_names <- all_video_names %>%
  rowwise() %>%
  mutate(vid_name = str_split(value,"[.]")[[1]][1])

# reset levels of vid_name in big detections array (very slow rowwise)
levels(detections$vid_name) <- all_video_names$vid_name

# join with metadata and flip the videos
d_all <- detections %>%
  left_join(meta, by='vid_name') %>%
  filter(!vid_name %in% flipped_videos$vid_name)

# check that we actually excluded the videos
num_orig_videos = length(unique(detections$vid_name))
num_videos_retained = length(unique(d_all$vid_name))
assert_that(num_videos_retained < num_orig_videos)

## All 6 of the video that were not in this file (but were in the detections file) happened to be 6 very bad quality videos; excluding from detections
exclude_bad_quality <- d_all %>%
  filter(!vid_name %in% right_side_up$video)

d_all <- d_all %>%
  filter(!vid_name %in% exclude_bad_quality$vid_name)

### Make detections into logical vectors and compute "person" as either face/hand
d_all$face_openpose = as.logical(d_all$face_openpose)
d_all$hand_openpose = as.logical(d_all$hand_openpose)
d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))

### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
vid_check <- d_all %>%
  filter(child_id == "S") %>%
  group_by(vid_name,vid_name, Databrary.Link) %>%
  summarize(prop_faces =mean(face_openpose))

high_faces <- vid_check %>%
  filter(prop_faces>.8)

## save this data so this doesn't have to be redone again
save(d_all, file = '../data/openpose_detections_filtered.RData')

### Instead, load preprocess and filtered detections
```{r}
load('../data/openpose_detections_filtered.RData')
```

### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(d_all$age_days)
max_age = max(d_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
d_all <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))

## How do face/hand detection vary by age? 
### Compute summary statistics
```{r}
summary_by_age <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)

### Plot faces x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth(span=10) + 
  ylab('Proportion Faces') + 
  xlab('Age bin (months)') +
  ylim(0,.5)
```

### Plot hands x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  ylab('Proportion Hands') + 
  xlab('Age bin (months)') +
  ylim(0,.5)
```

### Plot Faces - Hands x age x child:  Key plot for fausey comparison
```{r}
## faces - hands
ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)')

@@

## Look at trends in full dataset by location
```{r}
face_hand_by_location <- d_all %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_openpose), num_detect = length(face_openpose))  %>%
  filter(num_detect > 9000) %>% ## 9000 frames = 5 minutes of video at 30 fps %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

@@

### Plot faces and hands by location
```{r}
(plot_faces_loc = ggplot(faces_by_location_to_plot, aes(x = Location, y = mean, col=child_id)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .4, y = 0)) +
  geom_point(aes(x=Location, y=prop_faces, size=num_detect, alpha=.01)) +
  geom_point() +
  ylim(0,1) +
  coord_flip() + 
  ylab('Proportion Faces') +
  facet_grid(~child_id) )

(plot_hand_loc = ggplot(hands_by_location_to_plot, aes(x = Location, y = mean, col=age_day_bin)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(x=Location, y=prop_hands, size=num_detect, alpha=.01)) +
  geom_point() +
  ylim(0,1) +
  coord_flip() + 
  ylab('Proportion Hands') +
  facet_grid(~child_id) +
  theme(legend.position = "none"))

(plot_hands_vs_faces = ggplot(faces_vs_hands_to_plot, aes(x = Location, y = mean, col=age_day_bin)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect, alpha=.01)) +
  geom_point() +
  # ylim(0,1) +
  coord_flip() + 
  ylab('Proportion Faces - Hands') +
  facet_grid(~child_id) +  theme(legend.position = "none"))

# ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces)
```
## what percentage of the dataset is this? 
```{r}
percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
```

```{r}

# faces_by_location <- d_all %>%
#   filter(!is.na(Location)) %>%
#   filter(count_locations==1) %>%
#   group_by(Location,child_id,age_day_bin) %>%
#   summarize(prop_face = mean(face_openpose))  
# 
# ggplot(faces_by_location, aes(x = Location, y = prop_face, col=child_id)) + 
#   # geom_flat_violin() +
#   geom_boxplot() +
#   # geom_point() +
#   ylim(0,.8) +
#   ylab('Proportion Faces') +
#   coord_flip()

@@

```{r}
# face_vs_hands_location_all <- d_all %>%
#   filter(count_locations==1) %>%
#   filter(!Location=='NA') %>%
#   group_by(child_id,Location, age_day_bin) %>%
#   summarize(prop_faces = sum(face_openpose) / length(face_openpose), prop_hands = sum(hand_openpose) / length(hand_openpose), num_detect = length(face_openpose)) %>%
#   mutate(faces_vs_hands = prop_faces - prop_hands)
# 
# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=prop_faces, col=child_id, size=num_detect)) +
#   geom_point() +
#   # geom_smooth() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   ylab("Faces") +
#   facet_grid(~Location)
# 
# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=prop_hands, col=child_id, size=num_detect)) +
#   geom_point() +
#   # geom_smooth() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   ylab("Hands") +
#   facet_grid(~Location)
# 
# ggplot(face_vs_hands_location_all, aes(x=age_day_bin, y=faces_vs_hands, col=child_id, size=num_detect)) +
#   geom_point() +
#   # geom_smooth() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   ylab("Faces vs Hands") +
#   facet_grid(~Location)

@@

# Render out images based on annotations if desired
## True positives on faces?
```{r eval=FALSE}
faces_only_op_cor <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_tp/'))
for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
}

@@

## False positives on facs?
```{r eval=FALSE}
to_write <- m %>%
  filter(faces == FALSE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fp/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
}

@@

## False negatives on faces?
```{r eval=FALSE}
to_write <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == FALSE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fn/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
}

@@

>>>>

## Read in data 
### Load preprocessed and filtered detections
```{r}
load('../data/openpose_detections_filtered.RData') #d_all
load('../data/openpose_detections_filtered_cropped.RData') # d_cropped
```

### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(d_all$age_days)
max_age = max(d_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

d_all <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))
```

# Full dataset; all detection
## How do face/hand detection vary by age? 
### Compute summary statistics
```{r}
summary_by_age <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)

# under 24 months
summary_by_age_limited <- summary_by_age %>%
  filter(age_day_bin < 24.1)

@@

### Plot faces x age x child
```{r}
(faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth(span=10) + 
  ylab('Proportion Faces') + 
  xlab('Age bin (months)') +
  ylim(0,.5))
```

### Plot hands x age x child
```{r}
(hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  ylab('Proportion Hands') + 
  xlab('Age bin (months)') +
  ylim(0,.5))
```

### Plot Faces - Hands x age x child:  Key plot for fausey comparison
```{r}
## faces - hands
(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)'))
```

@@

## By location
### Summarize faces vs hands by location
```{r}
face_hand_by_location <- d_all %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_openpose), num_detect = length(face_openpose))  %>%
  filter(num_detect > 9000) %>% ## 9000 frames = 5 minutes of video at 30 fps %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

@@

### Plot faces and hands by location
```{r}
(plot_faces_loc = ggplot(faces_by_location_to_plot, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(0,.6) +
  coord_flip() + 
  ylab('Proportion Faces')+
   theme(legend.position = "none"))

(plot_hand_loc = ggplot(hands_by_location_to_plot, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(0,.6) +
  coord_flip() + 
  ylab('Proportion Hands') +
  theme(legend.position = "none"))

(plot_hands_vs_faces = ggplot(faces_vs_hands_to_plot, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(-.4,.4) +
  coord_flip() + 
  ylab('Proportion Faces - Hands'))

ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces, nrow=1)
```

### what percentage of the dataset is this? 
```{r}
percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
```

# Cropped analysis
## Faces vs hands
### Summary statistics
```{r}
summary_by_age_cropped <- d_cropped %>%
  group_by(age_day_bin,child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect)

summary_by_age_cropped_limited <- summary_by_age_cropped %>%
  filter(age_day_bin < 24.1)
```

### Plot hands x age x child
```{r}
(hands_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  ylab('Proportion Hands (Cropped)') + 
  xlab('Age bin (months)') +
  ylim(0,.5))
```

### Plot faces vs. hands for cropped frames
```{r}
(face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.4) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)') +
  ylim(-.3, .3) +
  ggtitle('(B). Upper 60% of FOV'))

(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.4) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)') +
  ylim(-.3, .3) +
  theme(legend.position = "none") +
  ggtitle('(A). Entire FOV'))

ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)

@@

```{r}
ggplot(summary_by_age_cropped_limited, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10, method='lm') + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands (CROPPED)') + 
  xlab('Age (months)')

ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)

@@

### Side by side plots for cropped comparison
```{r}
ggarrange(hands, hands_cropped, nrow=1)
ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)

@@

## By location
### Summarize

### Load SAYCAM metadata from csv file
```{r}
metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"

@@

### Join with cropped datasets and summarize
```{r}
face_hand_by_location_cropped <- d_cropped %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected_cropped), num_detect = length(hand_detected_cropped))  %>%
  filter(num_detect > 9000) %>% ## 9000 frames = 5 minutes of video at 30 fps %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

hands_by_location_to_plot_cropped <- face_hand_by_location_cropped %>%
  multi_boot_standard(col="prop_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
  mutate(Location = fct_reorder(Location, mean))

faces_by_location_to_plot_cropped <- face_hand_by_location_cropped %>%
  multi_boot_standard(col="prop_faces") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
  mutate(Location = fct_reorder(Location, mean))

faces_vs_hands_to_plot_cropped <- face_hand_by_location_cropped %>%
  multi_boot_standard(col="faces_vs_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
  mutate(Location = fct_reorder(Location, mean))

@@

### Plot cropped detections by location
```{r}
(plot_faces_loc_cropped = ggplot(faces_by_location_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(0,.6) +
  coord_flip() + 
  ylab('Proportion Faces')+
   theme(legend.position = "none"))

(plot_hand_loc_cropped = ggplot(hands_by_location_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(0,.6) +
  coord_flip() + 
  ylab('Proportion Hands') +
  theme(legend.position = "none"))

(plot_hands_vs_faces_cropped = ggplot(faces_vs_hands_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(-.4,.4) +
  coord_flip() + 
  ylab('Proportion Faces - Hands'))

# ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces)
ggarrange(plot_faces_loc_cropped, plot_hand_loc_cropped,plot_hands_vs_faces_cropped, nrow=1)
# ggarrange(plot_hands_vs_faces,plot_hands_vs_faces_cropped, nrow=1)

# Inferential statistics
### Entire age range
```{r}
summary_by_age_cropped$num_detect <- scale(summary_by_age_cropped$num_detect)

model_cropped <- glmer(prop_faces - prop_hands ~ age_day_bin + (1 | child_id), data = summary_by_age_cropped_limited)
summary(model_cropped)
```

### Full dataset
```{r}
summary_by_age_cropped_limited$num_detect <- scale(summary_by_age_cropped_limited$num_detect)

model_limited_cropped <- glmer(prop_faces - prop_hands ~ age_day_bin + num_detect + (1 | child_id), data = summary_by_age_cropped_limited)
summary(model_limited_cropped)

# Analyze most frequent activities by location
```{r}
frames_by_video <- d_all %>%
  group_by(vid_name) %>%
  summarize(num_frames = n())

activity_by_location <- meta %>%
  filter(!is.na(Location)) %>%
  filter(!Activity=='N/A') %>%
  filter(!is.na(Activity)) %>%
  filter(!Location=='N/A') %>%
  filter(count_locations==1) %>%
  select(vid_name, Location, Activity) %>%
  mutate(Activity = strsplit(as.character(Activity), ",")) %>% 
  unnest(Activity)

# fix typo in annotations
activity_by_location$Activity[activity_by_location$Activity=='Talking Walk']='Taking Walk'
```

### Plot activities by context
```{r}
activity_contexts <-  activity_by_location %>%
  left_join(frames_by_video) %>%
  filter(!Activity=='N/A') %>%
  group_by(Location,Activity) %>%
  summarize(count_frames = sum(num_frames)) %>%
  filter(count_frames > 9000)

ggplot(activity_contexts, aes(Location, y=Activity)) +
  geom_tile(aes(fill = count_frames)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  coord_flip()

### 2020-01-15 analysis/detector_validation.Rmd
separate out preprocessing of main datasets

prf_by_location_faces$age_day_bin  = as.numeric(as.character(prf_by_location_faces$age_day_bin))
ggplot(prf_by_location_faces, aes(x=age_day_bin, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  facet_grid(~Location)
  geom_smooth()  +
  ylab('F-score - Face detection')
```

>>>>

prf_by_location_faces$age_day_bin  = as.numeric(as.character(prf_by_location_faces$age_day_bin))
ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=age_day_bin)) +
  geom_point(alpha=.5) +
  ylab('F-score - Face detection') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
